Make any stupid plot you want

### 2020-12-14 draft/sections/math.tex
sheaves?

%not sure what's supposed to happen w/ sheafs here
% add U ^ V + intersection to get section on union which is condition of sheafs.

\subsection{Prerender Space}
\label{sec:display}

@@

The artist is a mapping from the $\Gamma(E)$ space of all datasets with a shared $F$ and $K$ to a pre-render space $H$ with display target properties $D$ and visualization structure $S$.

@@

As described in section~\ref{sec:display}, $rho: S \rightarrow H$ is composed of subfunctions that are dependent on the prerender fiber $D$. In the case of a screen where $D=\mathbb{R}^{7}$

\begin{equation}
    \rho (u, v) = (\rho_X(u, v), \rho_Y (u, v), \rho_Z (u, v), \rho_B (u, v), \rho_G (u, v), \rho_B (u, v), \rho_A (u, v))
\end{equation}

where $(u,v)$ are coordinates of a point on $S$. The map reduce function $Q: F\rightarrow \rho$ builds $\rho$ functions on $S$ by compositing $\nu_{param}: c \mapsto \rho_{d \in D}$ functions that map data in some field $c$ to a subset of visual variables such as position or color\cite{bertinIIPropertiesGraphic2011, munznerChDataAbstraction} that are identified as parameters to the artist function.

@@

$Q$ composites $\nu$ functions because multiple parameters can target the same field in $D$, for example $\nu_{ypos}$ and $\nu_{linewidth}$ together determine the y position of a line drawn on screen such that $Q: \nu_{ypos}, \nu_{linewidth} \rightarrow \rho_{Y}$

>>>>

%not sure what's supposed to happen w/ sheafs here
% add U ^ V + intersection to get section on union which is condition of sheafs. 
\subsection{Prerender Space}
\label{sec:display}

@@

The artist is a mapping from the sheaf $O(E)$ which a dataset to a pre-render space $O(H)$ with display target properties $D$ and visualization structure $S$.

@@

where $A$ is composed of an asthethic mapping $\Xi = Q \circ \nu$ that builds the prerender render function $rho: S \rightarrow H$ functions described in section~\ref{sec:display}. $\XI$ builds $\rho$ functions on $S$ by compositing $\nu_{param}: c \mapsto \rho_{d \in D}$ functions that map data in some field $c$ to a subset of visual variables such as position or color\cite{bertinIIPropertiesGraphic2011, munznerChDataAbstraction} that are identified as parameters to the artist function.

@@

$Q$ composites $\nu$ functions because multiple parameters can target the same field in $D$, for example $\nu_{ypos}$ and $\nu_{linewidth}$ together determine the y position of a line drawn on screen such that $Q: \nu_{ypos}, \nu_{linewidth} \rightarrow \rho_{Y}$. The artist is 
\begin{equation}
\begin{tikzcd}
    \iota^{*}E \arrow[rd, "\Xi" description] & H \arrow[d, "\rho^{-1}" description, bend right]                         \\
    U \arrow[u, "\tau" description]          & S \arrow[u, "\rho" description, bend right] \arrow[l, "\xi" description]
\end{tikzcd}
\end{equation}
